Portal Forecast

### 2017-08-11 index.Rmd
Change references to column names to match new standard in PortalData

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moon_file = portalr::FullPath('PortalData/Rodents/moon_dates.csv', 
                                                  '~')
new_moons = read.csv(new_moon_file)
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "Period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

@@

forecast_viz(obs_data = obs_data_newmoon,
             obs_date_col_name = "NewMoonNumber",
             obs_val_col_name = "total",
             for_data = for_data,
             for_date_col_name = "NewMoonNumber",
             for_val_col_name = "estimate",
             for_model_name = "ensemble",
             for_lowerpi_col_name = "LowerPI",
             for_upperpi_col_name = "UpperPI",
             start_newmoon = 300)
```

@@

for (species in as.vector(most_abund_sp$species)) {
  species_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "NewMoonNumber",
               obs_val_col_name = species,
               for_data = for_data,
               for_date_col_name = "NewMoonNumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(species_forecast)
}
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moon_file = portalr::FullPath('PortalData/Rodents/moon_dates.csv', 
                                                  '~')
new_moons = read.csv(new_moon_file)
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

@@

forecast_viz(obs_data = obs_data_newmoon,
             obs_date_col_name = "newmoonnumber",
             obs_val_col_name = "total",
             for_data = for_data,
             for_date_col_name = "newmoonnumber",
             for_val_col_name = "estimate",
             for_model_name = "ensemble",
             for_lowerpi_col_name = "LowerPI",
             for_upperpi_col_name = "UpperPI",
             start_newmoon = 300)
```

@@

for (species in as.vector(most_abund_sp$species)) {
  species_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "newmoonnumber",
               obs_val_col_name = species,
               for_data = for_data,
               for_date_col_name = "newmoonnumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(species_forecast)
}
```
